---
title: "dogr Vignette"
output: html_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(warnings=FALSE)
```
###*2016-11-30*

###Package Description

The dogr package is designed to help in basic canine behavior statistical analysis. It is useful for analyzing variables related to how and when a dog asks to go outside. Its functions have the ability to provide frequency tables, box plots, and scatter plots of canine behavior variables such as extra measures taken when asking to go outside and how many times they asked, as well as other contributing factors such as the temperature outside, if the owner was already outside before the dog asked, and if rain or snow is present. 

The dogr package requires the following packages to already be installed in R by the user: googlesheets, stats, graphics

###Data
My dog (Toby) has been super annoying lately with asking to go outside way more than he has in the past. I am going to track how frequently he asks to go outside per day, how he asks to go outside (scratching at the door, growling, stomping his feet, jumping on me, etc.), how long on average he spends outside per day, and additional factors like temperature, weather, if I am already outside, etc. I am predicting his little tantrums will decrease as the temperature goes down and the weather becomes increasingly worse. I also predict he will want to go out more often when I am outside and that he will ask to go out more frequently just to get treats when he comes back in.

Variables:
1) Date: "Date"
2) Day of the week: "Day_week"
3) Number of times asked to go outside: "No_times_ask"
4) Extra measures taken to get my attention – growling, stomping, barking: "Extra_measures"
5) Approximate total time spent outside – minutes: "Total_time"
6) I am also/already outside – Y/N: "Owner_outside"
7) Number of times he actually needed to go outside/use the bathroom: "Actual_times_used"
8) Average temperature outside – Fahrenheit: "Temp"
9) Rain/snow – Y/N: "Rain_snow"
10) Number of treats received per day: "No_treats"
11) If he saw an animal out the window: "Animal"

##Get toby dataset
###Install googlesheets package
```{r warning=FALSE, message=FALSE}
library(googlesheets)
```
###Load toby datset
*The following code does not work - I'm guessing it's an authorization issue? - so I am including the load .csv code just so the rest of the page will run. I will figure this issue out before the last homework. I'm sorry!*
t <- gs_title("Toby_data")
t %>% gs_browse()
toby <- gs_read(t, header=TRUE)

```{r}
toby <- read.csv("~/Desktop/Toby_data.csv", header=TRUE)
```

##Take a look at the data
```{r}
library(utils)
head(toby)
```

##Convert variables as needed
```{r}
toby$No_times_ask <- as.numeric(toby$No_times_ask)
toby$Total_time <- as.numeric(toby$Total_time)
toby$Actual_times_used <- as.numeric(toby$Actual_times_used)
toby$Temp <- as.numeric(toby$Temp)
toby$No_treats <- as.numeric(toby$No_treats)
toby$Rain_snow <- as.factor(toby$Rain_snow)
toby$Animal <- as.factor(toby$Animal)
```

##Summaries of continuous variables
```{r}
library(base)
summary(toby$Total_time)
summary(toby$Actual_times_used)
summary(toby$No_times_ask)
summary(toby$Temp)
```

###Summaries of categorical variables
```{r warning=FALSE, message=FALSE}
library(Hmisc)
describe(toby$Extra_measures)
describe(toby$Day_week)
```

##Look at a couple of plots
```{r message=FALSE}
library(Hmisc)
library(ggplot2)
plot(x=toby$No_times_ask, y=toby$Temp, main="Number of times asked to go outside vs.
     Temperature", xlab="Number of times asked", ylab="Temperature (Farenheit)")
plotA <- qplot(No_times_ask, data=toby, geom="density",
      fill=Rain_snow, alpha=I(.5), main="Number times asked vs. Rain/Snow", xlab="Number times asked", ylab="Density")
plotA
plotC <- qplot(No_times_ask, data=toby, geom="density",
      fill=Animal, alpha=I(.5), main="Number times asked vs. Animal presence", xlab="Number times asked", ylab="Density")
plotC
```

*In order for qplot 'fill=...' code to work, fill variable must be coded as FACTOR*

##Run some t-tests
```{r warning=FALSE}
attach(toby)
t.test(No_times_ask, Temp)
t.test(Temp, Total_time)
```

##dogr Functions
###fdogown
The fdogown function in the dogr package generates a basic frequency table of the number of times a dog requests to go outside versus a specified categorical variable in the canine dataset. 

###measureplot
The measureplot function in the dogr package generates a basic box plot of a categorical variable of extra measures taken - i.e. growling, scratching at the door, whining, etc. - and a specified continuous variable such as the temperature outside.

###tempplot
The tempplot function in the dogr package generates a basic scatter plot of a continuous variable of the number of times a dog asks to go outside and a specified second continuous variable such as the temperature outside.

###timebox Function
The timebox function in the dogr package generates a basic box plot of total time the dog spends outside versus a specified categorical variable in the canine dataset.


