---
title: "dogr Vignette"
output: html_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(warnings=FALSE)
```
###*2016-11-30*

###Package Description

The dogr package is designed to help in basic canine behavior statistical analysis. It is useful for analyzing variables related to how and when a dog asks to go outside. Its functions have the ability to provide frequency tables, box plots, and scatter plots of canine behavior variables such as extra measures taken when asking to go outside and how many times they asked, as well as other contributing factors such as the temperature outside, if the owner was already outside before the dog asked, and if rain or snow is present. 

The dogr package requires the following packages to already be installed in R by the user: googlesheets, stats, graphics

###Data
My dog (Toby) has been super annoying lately with asking to go outside way more than he has in the past. I am going to track how frequently he asks to go outside per day, how he asks to go outside (scratching at the door, growling, stomping his feet, jumping on me, etc.), how long on average he spends outside per day, and additional factors like temperature, weather, if I am already outside, etc. I am predicting his little tantrums will decrease as the temperature goes down and the weather becomes increasingly worse. I also predict he will want to go out more often when I am outside and that he will ask to go out more frequently just to get treats when he comes back in.

Variables:
1) Date: "Date"
2) Day of the week: "Day_week"
3) Number of times asked to go outside: "No_times_ask"
4) Extra measures taken to get my attention – growling, stomping, barking: "Extra_measures"
5) Approximate total time spent outside – minutes: "Total_time"
6) I am also/already outside – Y/N: "Owner_outside"
7) Number of times he actually needed to go outside/use the bathroom: "Actual_times_used"
8) Average temperature outside – Fahrenheit: "Temp"
9) Rain/snow – Y/N: "Rain_snow"
10) Number of treats received per day: "No_treats"
11) If he saw an animal out the window: "Animal"

##Get toby dataset
###Install googlesheets package
```{r warning=FALSE, message=FALSE}
library(googlesheets)
```
###Load toby datset
```{r warning=FALSE, message=FALSE}
t <- gs_url("https://docs.google.com/spreadsheets/d/1qCpVFeJJRBX59zaHjQlwXwpHoo9DW0Ur9LW2lo8m1UM/pubhtml")
toby <- gs_read(t, header=TRUE)
```

##Take a look at the data
```{r}
library(utils)
head(toby)
```

##Make sure continuous variables are numeric
```{r}
nnames <- c('No_times_ask', 'Total_time', 'Actual_times_used', 'Temp', 'No_treats')
toby[,nnames] <- lapply(toby[,nnames], as.numeric)
```

##Summaries of continuous variables
```{r}
library(base)
snames <- c('Total_time', 'Actual_times_used', 'No_times_ask', 'Temp')
lapply(toby[,snames], summary)
```

###Summaries of categorical variables
```{r warning=FALSE, message=FALSE}
library(Hmisc)
snames <- c('Extra_measures','Day_week')
lapply(toby[,snames], describe)
```

##Look at a couple of plots
```{r message=FALSE}
library(Hmisc)
library(ggplot2)
```
###Make sure categorical variables for fill plots are factor
```{r}
fnames <- c('Rain_snow', 'Animal')
toby[,fnames] <- lapply(toby[,fnames], as.factor)
```
###Plot
```{r}
plotA <- qplot(No_times_ask, data=toby, geom="density",
      fill=Rain_snow, alpha=I(.5), main="Number times asked vs. Rain/Snow", xlab="Number times asked", ylab="Density")
plotA
plotC <- qplot(No_times_ask, data=toby, geom="density",
      fill=Animal, alpha=I(.5), main="Number times asked vs. Animal presence", xlab="Number times asked", ylab="Density")
plotC
```

We can see here the dog requested to go out less when snow or rain was present. The data regarding if he saw an animal out the window first came back inconclusive.

##Run some t-tests
```{r warning=FALSE}
attach(toby)
t.test(No_times_ask, Temp)
t.test(Temp, Total_time)
```

The temperature outside looks to be correlated with both the number of times the dog asked to go out and the total time the dog spent outside.

##dogr Package
###fdogown Function
The fdogown function in the dogr package generates a basic frequency table of the number of times a dog requests to go outside versus a specified categorical variable in the canine dataset. 
```{r warning=FALSE, message=FALSE}
library(devtools)
library(dogr)
fdogown(x=toby$No_times_ask, y=toby$Owner_outside)
```
The average number of times the dog asked to go out corresponded with the 3 times the owner was already present outside - this was unexpected. We expected to see the dog request more times in a day if he saw his owner already outside.

###measureplot Function
The measureplot function in the dogr package generates a basic box plot of a categorical variable of extra measures taken - i.e. growling, scratching at the door, whining, etc. - and a specified continuous variable such as the temperature outside.
```{r}
measureplot(x=factor(toby$Extra_measures), y=toby$Temp)
```

###tempplot Function
The tempplot function in the dogr package generates a basic scatter plot of a continuous variable of the number of times a dog asks to go outside and a specified second continuous variable such as the temperature outside.
```{r}
tempplot(x=toby$No_times_ask, y=toby$Temp)
```

The data shows the dog for the most part wanted to go outside more frequently when the temperature was between 40 and 75. 

###timebox Function
The timebox function in the dogr package generates a basic box plot of total time the dog spends outside versus a specified categorical variable in the canine dataset.
```{r}
timebox(x=toby$Rain_snow, y=toby$Total_time, xlab="Rain/Snow present", ylab="Total time            spent outside (minutes)", main="Total time spent outside vs. Rain/Snow present")
```

###ddogr Function
The ddogr function generates a dual-use plot showing the total time in minutes a dog spends outside each time they go out versus a specified continuous variable in the dataset such as temperature in Farenheit.
```{r}
ddogr(toby$Total_time, toby$Temp)
```


